%-------------------------------------------------------------------------------
%PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%-------------------------------------------------------------------------------

\documentclass[10pt,letterpaper]{article} % Font size (10-12pt) and
                                % paper size (a4paper, letterpaper,
                                % legalpaper, etc)

\include{Resume_sty} % Include structure.tex which contains packages
                    % and document layout definitions

\hyphenation{Some-long-word} % Specify custom hyphenation points in
                             % words with dashes where you would like
                             % hyphenation to occur, or alternatively,
                             % don't put any dashes in a word to stop
                             % hyphenation altogether

\begin{document}

%-------------------------------------------------------------------------------
%NAME AND CONTACT INFORMATION
%-------------------------------------------------------------------------------

\maintitle{Benjamin Stokes, Ph.D.}{}

\noindent\textsmaller{+}1 (801) 839-8993\bull
\href{http://www.linkedin.com/in/benjamintstokes}
{linkedin.com/in/benjamintstokes}\\
\href{mailto:benjamin.t.stokes@gmail.com}{benjamin.t.stokes@gmail.com}\bull
\href{https://github.com/benjamin-stokes}
{github.com/benjamin-stokes}

\spacedhrule{0.9em}{-0.4em}

%-------------------------------------------------------------------------------
%SUMMARY SECTION
%-------------------------------------------------------------------------------

\roottitle{Summary}

\vspace{-0.3em}
\bodytext{\textit{I am a data-oriented product architect
    and a team leader with extensive experience
    leveraging data to identify new business
    opportunities and operationalize big ideas.
    Through a high degree of creative
    persistence, I have successfully tackled extremely difficult
    problems.  Specific areas of prior expertise include:}
  \begin{multicols}{2}  % Start a two-column layout
  \begin{itemize}
\item Machine learning solutions
\vspace{-0.3em}\item Minimum viable product specification
\vspace{-0.3em}\item Artificial intelligence quality assurance
\vspace{-0.3em}\item Numerical modeling and simulations
\vspace{-0.3em}\item Algorithm development and implementation
\item Product evangelism
\vspace{-0.3em}\item Customer engagement platforms
\vspace{-0.3em}\item Strategic problem solving
\vspace{-0.3em}\item International collaboration
\vspace{-0.3em}\item Public Presentation
\vspace{-0.3em}  \end{itemize}
\end{multicols}}

\spacedhrule{0.5em}{-0.4em}

%-------------------------------------------------------------------------------
%SKILLS SECTION
%-------------------------------------------------------------------------------

\roottitle{Skills}

\inlineheadsection
    {Computer Languages:}
    {\acr{R}, Python, Go, \acr{C}, \acr{C++}, Bash, \LaTeX,
      Java, \acr{FORTRAN}, \textit{(whatever else is needed)}
    }
    \inlineheadsection
        {Data Management, Statistical Analysis, and Machine Learning:}
        {\acr{R}, \acr{SQL} Server, Redshift, Tableau, Excel}

    \inlineheadsection
        {Distributed Systems and Virtualization:}
        {\acr{AWS}, Azure, \acr{VM}ware, Hadoop, MapReduce, Spark}

    \inlineheadsection
        {Frameworks, Environments, and Operating Systems:}
        {Linux, Windows, Azure DevOps, Google Analytics and Adwords}

    \inlineheadsection
        {Natural languages:}
        {English \textit{(native proficiency)}, Russian
          \textit{(elementary proficiency)}, French \textit{(beginner)}}

\spacedhrule{2.0em}{-0.4em}

%-------------------------------------------------------------------------------
%CERTIFICATIONS SECTION
%-------------------------------------------------------------------------------

%\roottitle{Certification}

%\inlineheadsection
%    {Google AdWords Search Advertising}
%    { \textit{expired June 2018}}

%\spacedhrule{2.0em}{-0.4em}

%-------------------------------------------------------------------------------
%EXPERIENCE SECTION
%-------------------------------------------------------------------------------

\roottitle{Experience}

\headedsection
{\href{http://www.upshop.com}{Upshop}}
{\textsc{Tampa, Florida}} {

\headedsubsection
{\acr{VP} of Data Science}
{November 2021 -- Current}
{\bodytext{Upshop is a SaaS-based solutions provider for retail store operations
         with a primary focus on the grocery and convenience store sectors.
         As the \acr{VP} of Data Science,   I oversee a collaboration of data scientists, 
	data engineers, and business analysts that strives support our customer success
         and sales departments while simultaneously developing new machine learning 
	applications for our forecasting capabilities. Current initiatives include:

    \begin{itemize}
    \item \textit{\textbf {Expanding the feature set for the primary demand forecast.}}
	Forecasting instantaneous demand in the grocery sector is tremendously complex
	and requires the careful consideration of many endogenous and exogenous 
	factors.  To this end, we are continuously searching for additional features we
	can include in our models.  This initiative has led to a cumulative 30\% 
	improvement in our demand forecast accuracy.
    
	\item \textit{\textbf {Developing better for dashboards for internal and external 
	consumption.}}  Our clients and our internal teams rely upon the data we provide 
	them to make key business decisions on a daily basis.  As such, we strive to bring
	as much clarity as possible to our dashboards by actively collaborating with our 
	internal and external customers.

\end{itemize}}}}


\headedsection
{\href{http://www.nthrive.com}{nThrive}}
{\textsc{Layton, Utah}} {

\headedsubsection
{Director of Data Science}
{December 2019 -- November 2021}
{\bodytext{nThrive provides end-to-end revenue cycle management for the 
	full spectum of healthcare providers.  As the Director of Data Science,
	I led a team of data scientists, data engineers, and product analysts
	devoted to introducing machine learning into our product lines both through 
	product enhancements and new product offerings.  Key initiatives have 
	included:

    \begin{itemize}
    \item \textit{\textbf {Introducing ML-asssisted prioritization into work
	item queues.}}  Revenue cycle management often encounters instances where 
	workload exceeds the available resources.  By introducing machine learning
	into the prioritization process we reduced worker effort
	by up to 40\%
    
	\item \textit{\textbf {Utilizing machine learning to improve cash-flow 
	projections.}}  During the Covid pandemic, our clients struggled
	to make accurate projections of expected insurance payments. By introducing 
	predictive analytics into the payment projection process, we created an 
         adaptive solution that achieves a 10x reduction in aggregate error.

    \item \textit{\textbf{Engaging in AI evangelism both within the company and with the
	  client base.}} Many in the business community regard ML/AI with a combination 
           of apprehension and awe.  Through speaking engagements
	  and roundtables, I endeavored to make this exciting topic more approachable.
\end{itemize}}}}






%-------------------------------------------------------------------------------
%NAME AND CONTACT INFORMATION
%-------------------------------------------------------------------------------

\newpage
\maintitle{Benjamin Stokes, Ph.D.}{}

\noindent\textsmaller{+}1 (801) 839-8993\bull
\href{http://www.linkedin.com/in/benjamintstokes}
{linkedin.com/in/benjamintstokes}\\
\href{mailto:benjamin.t.stokes@gmail.com}{benjamin.t.stokes@gmail.com}\bull
\href{https://github.com/benjamin-stokes}
{github.com/benjamin-stokes}

\spacedhrule{0.9em}{-0.2em}

%-------------------------------------------------------------------------------
%EXPERIENCE SECTION (cont.)
%-------------------------------------------------------------------------------

\roottitle{Experience (cont.)}

\headedsection
{\href{http://www.sorenson.com}{Sorenson Communications}}
{\textsc{Taylorsville, Utah}} {

\headedsubsection
{Director of Data Science}
{July 2018 -- December 2019}
{\bodytext{Sorenson Communications is the premier provider of video
    relay \acr{ASL} interpretation services for the deaf and hard of
    hearing communities in the United States.  As the Director of
    Data Science, I spearheaded initiatives to introduce machine
    learning into the company's operational architecture.  
    The most significant of which was:

    \begin{itemize}
    \item \textit{\textbf {Upgrading the employee scheduling system.}}
    Providing professional interpreting services with 24/7 on-demand
    availability and minimal down-time has always been an
    extraordinary challenge for Sorenson.  By replacing specific
    business knowledge with machine learning algorithms, my team 
    created a much more adaptively resilient system that significantly improved
    efficiency while dictating over \$100 million in cost outlays.

\end{itemize}}}}

\headedsection
{\href{http://www.smash.ai}{Smash(ai)}}
{\textsc{Salt Lake City, Utah}} {


\headedsubsection
{Managing Data Scientist}
{July 2016 -- July 2018}
{\bodytext{Smash(ai) was an artificial intelligence solutions provider.
    Working on behalf of corporate clients, I oversaw and
    participated in the creation and implementation of impactful machine
    learning solutions.  These projects included:

    \begin{itemize}
    \item \textit{\textbf {Overseeing the development and
          implementation of an \acr{AI}-driven
          customer engagement platform.}} 

   \item \textit{\textbf {Devising a full-stack validation for a
          performance marketing optimization platform.}}
      
\end{itemize}}}}

\headedsection
{\href{http://www.finicity.com}{Finicity Data Services}}
{\textsc{Murray, Utah}} {

\headedsubsection
{Data Science Consultant}
{April 2016 -- July 2016}
{\bodytext{Finicity was a rapidly expanding fintech company whose core
    competency was financial account aggregation.  During my consulting
    stint, I spawned some exciting innovations that included:

    \begin{itemize}
    \item \textit{\textbf {Building an \acr{AI}-powered application for
          categorizing financial transactions.}}  
\end{itemize}}}}

\headedsection
{\href{http://www.utah.edu}{University of Utah}}
{\textsc{Salt Lake City, Utah}} {

\headedsubsection
{Research Faculty}
{May 2010 -- March 2016}
{\bodytext{I was a research collaborator with the
    \href{http://www.telescopearray.org}{Telescope Array} (\acr{TA})
    cosmic ray observatory.  The \acr{TA} collaboration
    developed extensive computational resources resulting in
    groundbreaking discoveries about the origin and composition of
    cosmic rays. In addition to supervising graduate and undergraduate 
	researchers, my personal achievements included:
    \begin{itemize}
    \item \textit{\textbf{Designing the primary framework for the
          Monte Carlo simulation of the \acr{TA} observatory.}}  I
      oversaw the integration of simulations provided
      by three independent research groups, and personally integrated 
	  40 years worth of legacy code,
      wrote 20,000 lines of new code, and innovated an entirely
      \href{http://arxiv.org/abs/1104.3182}{novel algorithmic
        approach}.  The
      \href{http://arxiv.org/abs/1403.0644}{resulting simulations} were
      \href{http://arxiv.org/abs/1205.5067}{unprecedented} in detail
      and accuracy.
    \item \textit{\textbf {Developing a
          \href{http://arxiv.org/abs/1103.4643}{technique} for mapping
          and reducing parallel computations.}} 
   \item \textit{\textbf{Engaging in international collaboration.}}
     
 \end{itemize}}}}

%\headedsection
%{\href{http://www.rutgers.edu}{Rutgers, The State University of New Jersey}}
%{\textsc{Piscataway, New Jersey}} {

%\headedsubsection
%{Postdoctoral Associate}
%{July 2008 -- April 2010}
%{\bodytext{I first joined the \acr{TA} collaboration as a researcher
%    with the affiliated group at Rutgers University.  Relevant
%    experience included:
%    \begin{itemize}
%    \item \textit{\textbf{Learning to work remotely.}}  Spending the
%      majority of my time 3000~km from the rest of my research group
%      was an excellent opportunity to develop independence, clear
%      communication, and self-motivation.
%    \end{itemize}}}}

%\headedsection
%    {\href{http://manoa.hawaii.edu}{University of Hawai`i at M\={a}noa}}
%    {\textsc{Honolulu, Hawai`i}}{

%\headedsubsection
%{Junior Researcher}
%{September 2006 -- June 2008}
%{\bodytext{ At the Neuroscience and
%      \acr{MRI} Research Program, my primary responsibilities
%    included operationalizing \acr{fMRI} data analysis protocols
%    and performing clinical duties.  The most
%    important milestone for me was:
%    \begin{itemize}
%    \item \textit{\textbf{Successfully executing a major domain
%          change.}} In doing
%      so, I developed extensive strategies for efficiently tackling
%      unfamiliar problems.
%    \end{itemize}}}}

\spacedhrule{0.8em}{-0.4em}

%-------------------------------------------------------------------------------
%EDUCATION SECTION
%-------------------------------------------------------------------------------

\roottitle{Education}

\headedsection
{University of Utah}
{\textsc{Salt Lake City, Utah}} {

\headedsubsection
{Doctor of Philosophy in Physics}
{}{}

\headedsubsection
{Bachelor of Arts in Physics}
{}{}}


\spacedhrule{1.0em}{-0.4em}

%-------------------------------------------------------------------------------
%AWARDS SECTION
%-------------------------------------------------------------------------------

\roottitle{Awards}

\bodytext{\begin{itemize}
\item Outstanding Postdoctoral Researcher, \textit{University of Utah
    Department of Physics and Astronomy}
\vspace{-0.3em}\item U.S.\ Presidential Scholar, \textit{White House}
\vspace{-0.3em}\item National Science Scholar, \textit{U.S.\
  Department of Education}
\end{itemize}}

\spacedhrule{1.0em}{-0.4em}

%-------------------------------------------------------------------------------
%OTHER INTERESTS SECTION
%-------------------------------------------------------------------------------

\roottitle{Other Interests}

\bodytext{Among many passions, I am a four-season mountaineer, a
  classically-trained double bassist, and an internationally published
  amateur photographer.}

\end{document}
